---
title: "Agenda - R Workshop - ver2"
author: "Erik Marsja"
date: '2022-10-12'
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(readxl)
AgendaTable <- read_excel("C:/Users/EMarsja/OneDrive - Linköpings universitet/WSps/MDU-RKurs/AgendaTable.xlsx")
```

This is a rough agenda and I can change it according to wishes. 


```{r age, echo = FALSE, results='asis'}
knitr::kable(AgendaTable)
```

The first 30 minutes may be skipped or done quickly depending on the knowledge of the group.
I would like all of the people attending the Workshop/Course to:

- Install RStudio* (https://www.rstudio.com/)
- R (https://cran.r-project.org/)

I will also add all of you to a GitHub page where all the material can be downloaded prior to the Workshop/Course. 

If you have any problems contact me at erik.marsja@liu.se or erik.marsja@vti.se

A more detailed agenda as well as more instructions will be delivered closer to the Workshop.

*Or your preferred IDE if you already use R